### 2010-03-29 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: cite other users of universes.

For the structure of our data-types to be known, we crucially need the
ability to name them. \note{Pursuing this crappy analogy. Solving the type
presentation/representation debate would help solving that point.} To this
end, we will use a standard technique in dependently-typed programming: we
construct an ad-hoc universe. This technique dates back to Martin-L\"of
definition of type theory~\cite{martin-lof:itt}. Since then, it has been
fruitful as a programming 
technique~\cite{benke:universe-generic-prog,whoelse?}
\note{I would need some other example of universe construction for
  practical purposes}. 
We refer the reader to the Agda tutorial~\cite{norell:agda-tutorial} for a
pedagogical presentation of universe construction. 
\note{Is that really a motivating motivation for the usage of universe 
construction?}
\note{pwm: Surely ($\EnumU$, $\EnumT$) is a useful example of universes too.
Even if it doesn't show off their full power?}

>>>>

For the structure of our data-types to be known, we crucially need the
ability to name them. \note{Pursuing this crappy analogy. Solving the type
presentation/representation debate would help solving that point.} To this
end, we will use a standard technique in dependently-typed programming: we
construct an ad-hoc universe. This technique dates back to Martin-L\"of
definition of type theory~\cite{martin-lof:itt}. Since then, it has been
fruitful as a programming 
technique~\cite{benke:universe-generic-prog, oury:power-of-pi}
\note{Any idea of other papers?}. 
We refer the reader to the Agda tutorial~\cite{norell:agda-tutorial} for a
pedagogical presentation of universe construction. 
\note{Is that really a motivating motivation for the usage of universe 
construction?}
\note{pwm: Surely ($\EnumU$, $\EnumT$) is a useful example of universes too.
Even if it doesn't show off their full power?}
